Clustering: A pipeline to analyse time-course gene expression data

### 2019-03-22 scripts/03_clustering.Rmd
More fixes to model selection

    - *Within cluster similarity as a function of the number of cluster* XXX
      GAP statistics
    - *Stability analysis*: this method assumes that the results of the
      clustering will be more stable for the "true" number of clusters than
      for other number of clusters.

>>>>

    - *Within cluster similarity as a function of the number of cluster* XXX
      Elbow method
    - *Silhouette method*

    - *Stability analysis*: this method assumes that the results of the
      clustering will be more stable for the "true" number of clusters than
      for other number of clusters.

```{r running_clustering_on_all_k}
all_possible_n_clusters = 5:20
all_clustering = list()
wss_values = list()

i = 1
for(n_cluster in all_possible_n_clusters){
    clustering_results = moanin:::splines_kmeans(
	y, splines_model,
	n_clusters=n_cluster, random_seed=42,
	n_init=10)
    wss_values[i] = sum(clustering_results$WCSS_per_cluster)
    all_clustering[i] = clustering_results
    i = i + 1
}
```

### Elbow method

```{r elbow_method}

# function to compute total within-cluster sum of square

plot(all_possible_n_clusters, wss_values,
     type="b", pch=19, frame=FALSE, 
     xlab="Number of clusters K",
     ylab="Total within-clusters sum of squares")

```

### Average silhouette method

```{r average_silhouette_method}
# function to compute average silhouette for k clusters
average_silhoutte = function(labels, y) {
    silhouette_results = cluster::silhouette(unlist(labels[1]), dist(y))
    return(mean(silhouette_results[, 3]))
}

# extract the average silhoutte
average_silhoutte_values = list()
i = 1
for(i in 1:length(all_clustering)){
    labels = all_clustering[i]
    average_silhoutte_values[i] = average_silhoutte(labels, y)
    i = i + 1
}

plot(all_possible_n_clusters, average_silhoutte_values,
     type="b", pch=19, frame=FALSE,
     xlab="Number of clusters K",
     ylab="Average Silhouettes")
```
